\chapter*{Abstract}
% \addcontentsline{toc}{chapter}{Abstract}
\label{chap:abstract}
With significant advances in the \ac{AI} field, \ac{NLP} and contextual analysis techniques have been maturing greatly over the last few decades, with applications rising in various industries. Valuable applications of \ac{NLP} includes Automatic Speech Recognition systems, Sentiment Analysis and Natural Language Inference.

Although plenty of ink has been spilled on the subject of autonomous vehicles, the practical application of such systems will not take place overnight and there is a long way before we can see self-driving vehicles capable of handling all the driving tasks. Consequently, the present period is regarded as an intermediate stage which aims for more automation in the transportation process as a whole. Such stage will continue up until the switchover to $100\%$ self-driving vehicles is practical and achievable. 

The evolution of transport network operators to more automation requires an \ac{AI}-enabled control center room. In this project, we aim to enhance the capability of transportation systems, enabling them to understand human speech from vehicle driver input and trigger dispatcher actions automatically. As such, an \ac{AI} dispatcher agent needs to understand a message/call from a driver in order to trigger the necessary action, resulting in increased automation inside the control center. For this purpose we present a system which makes use of Automatic Speech Recognition, where the speech input from the driver is transcribed into text and fed into a Text Classifier Unit. The Text Classifier is trained to issue the dispatcher actions automatically. The resulting is a system with inputs as driver speech, and output as convenient dispatcher actions.
